Run-Time Monitoring with Adjustable Overheads Using Dataflow-Guided Filtering

### 2014-09-12 conclusion.tex
Added 10% overhead data.
Updates to abstract, intro, and conclusion.

Parallel run-time monitoring techniques are attractive solutions for improving
the reliability, security, and debugging capabilities of systems. In this
paper, we have presented an architecture that reduces the overheads of
monitoring through filtering and adjustable partial monitoring. This is done by
using a hardware dataflow tracking engine in order to track and filter out
monitoring for null metadata. In addition, the dataflow engine tracks invalid
metdata flows in order to enable partial monitoring without false positives.
Our experimental results show that filtering can greatly reduce the average
overheads of monitoring from 7x, 18x, and 11x for UMC, BC, and DIFT down to 4x
for UMC and BC and just 13\% for DIFT. With partial monitoring, we see that
with a 50\% overhead budget, BC can still achieve 83\% coverage and UMC can
still achieve 51\% coverage. Finally, we show that although source dropping can
achieve better coverage than unrestricted dropping when it works, it is not
able to match overhead targets as well as unrestricted dropping.

>>>>

Parallel run-time monitoring techniques are attractive solutions for improving
the reliability, security, and debugging capabilities of systems. In this
paper, we have presented an architecture that enables adjustable overheads through partial monitoring. 
The architecture uses a dataflow tracking engine to prevent false positives
through tracking invalidation information. In addition, we show how the
architecture can be extended to enable null metadata filtering.
Given this architecture, we explore design choices related to the dropping policy.
With partial monitoring, we see that with a 1.5x overhead target, BC can still
achieve 82\% average coverage and UMC can still achieve 43\% average coverage.
In addition, with a 1.5x overhead target, IMP shows less than 3\% error on
average.

% This is done by
% using a hardware dataflow tracking engine in order to track and filter out
% monitoring for null metadata. In addition, the dataflow engine tracks invalid
% metdata flows in order to enable partial monitoring without false positives.
% Our experimental results show that filtering can greatly reduce the average
% overheads of monitoring from 7x, 18x, and 11x for UMC, BC, and DIFT down to 4x
% for UMC and BC and just 13\% for DIFT. With partial monitoring, we see that
% with a 10\% overhead budget, BC can still achieve 82\% coverage and UMC can
% still achieve 32\% coverage. Finally, we show that although source-only dropping can
% achieve better coverage than unrestricted dropping when it works, it is not
% able to match overhead targets as well as unrestricted dropping.

### 2014-09-12 introduction.tex
Fix up citations.
Updates to abstract, intro, and conclusion.

% Programmable hardware monitors
These run-time monitors introduce performance, power, and energy overheads.
% Implementing run-time monitoring in software using binary instrumentation or
% other similar methods has been shown to introduce high overheads. For example,
% dynamic information flow tracking (DIFT) implemented in software suffers a 3.6x
% slowdown \cite{lift-micro06}. 
Implementing monitors in dedicated hardware has been shown to have small
performance impacts. For example, a dedicated hardware implementation of
dynamic information flow tracking (DIFT) shows performance
overheads of only 1.1\% \cite{dift-asplos04}. However, fixed hardware loses
the programmability of software, and cannot be updated or changed. It 
requires for monitors to be chosen and implemented at hardware design time.
Recent studies \cite{lba-isca08, ruwase-spaa08, paralog-asplos10, oases-sigops09} have proposed using parallel cores in a
multi-core system to perform monitoring. This allows monitoring to be done
using parallel hardware while having the flexibility and programmability of
software. However, due to the multiple cycles it may take for software to
monitor an instruction, the overheads can easily increase execution time
several fold.
% Two optimizations
Since these overheads can be prohibitive for run-time use, we propose to enable
partial monitoring in order to reduce the overheads.

@@

% Evaluation
In order to evaluate our approach, we applied it to 3 different monitoring
techniques. These monitoring techniques vary in what events they monitor, the
size and semantics of their metadata, and the operations performed on metadata.
Our experiments show that filtering reduces the average overhead of these
monitors from 7-18x down to 13-300\%.
In addition, with partial monitoring, for the monitoring schemes which still
see average overheads of 300\%, we show that with just 10\% overheads, we can still
provide 32-82\% of coverage on average. By increasing the
overhead budget, this coverage rate can be increased.

% Section summary
This paper is organized as follows. Section~\ref{sec:monitoring} presents the
baseline parallel run-time monitoring model that this paper assumes.
Section~\ref{sec:dropping} discusses enabling partial monitoring using our dataflow tracking engine.
Section~\ref{sec:policies}
investigates the design space for dropping decisions for partial monitoring.
Section~\ref{sec:filtering} shows how the dataflow tracking engine can be extended to filter null metadata.
Section~\ref{sec:evaluation} presents our evaluation methodology and
results. Finally, we discuss related work in Section~\ref{sec:related} and
conclude in Section~\ref{sec:conclusion}.

>>>>

% Programmable hardware monitors
% These run-time monitors introduce performance, power, and energy overheads.
% Implementing monitors in dedicated hardware has been shown to have small
% performance impacts. For example, a dedicated hardware implementation of
% dynamic information flow tracking (DIFT) shows performance
% overheads of only 1.1\% \cite{dift-asplos04}. However, fixed hardware loses
% the programmability of software, and cannot be updated or changed. It 
% requires for monitors to be chosen and implemented at hardware design time.
% Recent studies \cite{lba-isca08, ruwase-spaa08, paralog-asplos10, oases-sigops09} have proposed using parallel cores in a
% multi-core system to perform monitoring. This allows monitoring to be done
% using parallel hardware while having the flexibility and programmability of
% software. However, due to the multiple cycles it may take for software to
% monitor an instruction, the overheads can easily increase execution time
% several fold.
% % Two optimizations
% Since these overheads can be prohibitive for run-time use, we propose to enable
% partial monitoring in order to reduce the overheads.

Previous studies have explored various design points in terms of efficiency,
flexibility, and hardware costs for implementing run-time monitors. Custom
hardware designs that target a single or narrow-range of monitors have been
shown to have low performance overheads. On the other hand, flexible systems
that support a range of monitors have shown much higher overheads. In this
paper, we explore a new trade-off dimension for run-time monitoring designs. We
propose to enable low overhead monitors without sacrificing flexibility by
using partial monitoring. This instead allows a trade-off between overheads and
monitoring coverage or accuracy.

@@

% Evaluation
In order to evaluate our approach, we applied it to 4 different monitoring
techniques. These monitoring techniques vary in what events they monitor, the
size and semantics of their metadata, and the operations performed on metadata.
% Our experiments show that filtering reduces the average overhead of these
% monitors from 7-18x down to 13-300\%.
% In addition, with partial monitoring, for the monitoring schemes which still
% see average overheads of 300\%, we show that with just 10\% overheads, we can still
% provide 32-82\% of coverage on average. By increasing the
% overhead budget, this coverage rate can be increased. 
These monitors show baseline overheads of 4-16x without null metadata filtering
and 1.1-4.3x after null metadata filtering.  Our results show that with 1.5x
overhead, coverage of 43-82\% on average can still be achieved and that
overhead and coverage can be varied to create a trade-off.

% Section summary
This paper is organized as follows. Section~\ref{sec:monitoring} presents the
baseline parallel run-time monitoring model that this paper assumes.
Section~\ref{sec:dropping} discusses enabling partial monitoring using our dataflow tracking engine.
Section~\ref{sec:policies}
investigates the design space for dropping decisions for partial monitoring.
Section~\ref{sec:evaluation} presents our evaluation methodology and
results. Finally, we discuss related work in Section~\ref{sec:related} and
conclude in Section~\ref{sec:conclusion}.

### 2014-09-12 title.tex
revised Section 2 to better motivate adjustable monitoring
Updates to abstract, intro, and conclusion.

\title{
Dataflow-Guided Filtering for Efficient and Adjustable Run-Time Monitoring
}

@@

Recent studies have proposed various parallel run-time monitoring techniques to
improve the reliability, security, and debugging capabilities of computer
systems. However, these run-time monitors can introduce large performance and energy
overheads, especially when performed on programmable cores.
%Traditionally, these overheads have been an
%all-or-nothing cost; monitoring cannot be used if the overheads are considered
%too large.  
In this paper, we introduce a hardware dataflow tracking engine that can be
used to filter out unnecessary monitoring and enable adjustable partial monitoring.
The dataflow engine can identify events with null metadata so that they can
be filtered out. To further reduce the overhead of monitoring, we propose
to enable a trade-off between monitoring coverage and overhead by dropping certain
monitoring operations. For this partial monitoring, the dataflow engine is used
to track dropped monitoring flows so that false positives can be avoided.
Given the architecture, we also investigate how the dropping decisions should be
made for partial monitoring and show that there exists a trade-off between closely
matching an overhead target and the coverage that can be achieved.
% Our experiments show that the system is able to
% closely meet the target overhead and achieve significant monitoring coverage
% for reasonable overhead targets.
The experimental results show that filtering can significantly reduce monitoring
overheads from XX\%-XX\% on average, depending on the monitoring scheme, to
XX\%-XX\%. Additionally, the partial monitoring is shown to still achieve XX\% coverage 
only with a 10\% overhead target.

>>>>

\title{
%Dataflow-Guided Filtering for Efficient and Adjustable Run-Time Monitoring
%Efficient and Adjustable Run-Time Monitoring Using Dataflow-Guided Filtering
Run-Time Monitoring with Adjustable Overheads Using Dataflow-Guided Filtering
}

@@

Recent studies have proposed various parallel run-time monitoring techniques to
improve the reliability, security, and debugging capabilities of computer
systems. However, these run-time monitors can introduce large performance and energy
overheads, especially when performed on programmable cores.
%Traditionally, these overheads have been an
%all-or-nothing cost; monitoring cannot be used if the overheads are considered
%too large.  
In this paper, we introduce a hardware dataflow tracking engine that enables
adjustable overheads through partial monitoring. This allows a trade-off to be
made between monitoring coverage and overhead. We show how this dataflow engine
can be extended to filter out monitoring operations associated with null
metadata in order to reduce overheads.
% In this paper, we introduce a hardware dataflow tracking engine that can be
% used to filter out unnecessary monitoring and enable adjustable partial monitoring.
% The dataflow engine can identify events with null metadata so that they can
% be filtered out. To further reduce the overhead of monitoring, we propose
% to enable a trade-off between monitoring coverage and overhead by dropping certain
% monitoring operations. For this partial monitoring, the dataflow engine is used
% to track dropped monitoring flows so that false positives can be avoided.
Given this architecture, we also investigate how the dropping decisions should be
made for partial monitoring and show that there exists a trade-off between closely
matching an overhead target and the coverage that can be achieved.
Our experimental results show that overheads can be reduced from 4-16x on
average to 1.5x while still achieving 43-82\% coverage.
